\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{\vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Fernando Ruiz Mazo} \\ \vspace{1pt}
  \small +34 619 51 21 47 $|$ \href{mailto:fruizmazo@gmail.com}{fruizmazo@gmail.com} $|$ 
  \href{https://linkedin.com/in/fernando-ruiz-mazo-80700321a}{linkedin.com/in/fernando-ruiz-mazo} $|$
  \href{https://github.com/ferruimaz}{github.com/ferruimaz}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Cambridge}{Cambridge, UK}
      {MPhil in Mathematics, (La Caixa Postgraduate Fellowship)}{Oct 2025 -- Oct 2026}
    \resumeSubheading
      {University of Warwick}{Coventry, UK}
      {BSc in Mathematics, Fist Class (Erasmus and Santander Scholar)}{Sep 2024 -- Jun 2025}
    \resumeSubheading
      {Universidad de Sevilla}{Seville, Spain}
      {BSc in Mathematics, Final Average: 9.33 / 10 (26/30 modules passed with honors)}{Sep 2021 -- Jun 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Researcher in Amortized Bayesian Inference}{Cambridge, UK}
      {University of Cambridge, Magdalene College}{Oct 2025 -- Oct 2026}
      \resumeItemListStart
        \resumeItem{Conducting research under Prof. Sergio Bacallado on scalable and amortized Bayesian inference frameworks, with emphasis on Neural Processes.}
        \resumeItem{Designing robust posterior estimation algorithms that generalize across tasks in meta-learning.}
      \resumeItemListEnd

    \resumeSubheading
      {Research Assistant}{Helsinki, Finland}
      {Aalto Science Institute}{Jul 2025 -- Oct 2025}
      \resumeItemListStart
        \resumeItem{Selected from more than 1700 international applicants for advanced machine learning research.}
        \resumeItem{Collaborating with Dr. Vikas Garg on Post-Bayesian methods for creating more robust Neural Processes.}
      \resumeItemListEnd

    \resumeSubheading
      {MEFP Research Scholar}{Seville, Spain (Hybrid)}
      {Universidad de Sevilla}{Sept 2024 -- Jul 2025}
      \resumeItemListStart
        \resumeItem{Received national merit-based research fellowship from Spanish Ministry of Education.}
        \resumeItem{Worked on a unified mathematical framework for feature selection using quiver representations.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Artificial Intelligence Course Project}{Oxford, UK}
      {University of Oxford, Lady Margaret Hall }{Jul 2023 - Aug 2023}
      \resumeItemListStart
        \resumeItem{Built time-series forecasting models in Python for mean-reversion signals and trend analysis using regression and neural networks.}
        \resumeItem{Applied convolutional neural network architectures to detect spatiotemporal patterns in simulated financial sequences.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Grants}
  \resumeSubHeadingListStart
    \resumeSubheading
      {La Caixa Postgraduate Fellowship}{Cambridge, UK}
      {University of Cambridge}{Oct 2025 -- Oct 2026}
      \resumeItemListStart
        \resumeItem{Selected as one of 100 awardees from more than 1\,500 applicants ($<7\%$ acceptance); fellowship covers full tuition at the University of Cambridge and provides an extra £22,750 annual stipend.}
        \resumeItem{Finances my MPhil in Mathematics and confers lifelong membership in the international \textit{la~Caixa Fellows} network.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
     \textbf{Languages}{: Python, R, MATLAB, Haskell, LaTeX} \\
     \textbf{Libraries}{: TensorFlow, PyTorch, Keras, Pandas, Scikit-learn, NumPy, SciPy} \\
     \textbf{Tools}{: Jupyter, reproducible research workflows}
  }}
\end{itemize}

\end{document}
